Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-03 sattose/paper.tex
Added the todo package
Did something with Ana's feedback in the abstract

\begin{abstract}
Duplication in source code can have a \todo{be more specific: what are examples of major impact?}major negative impact on the maintainability of source code. There are several techniques  to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system \todo{so? what is the link between these techniques and what you want to do?}. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. We look into \todo{why?} redefinitions for different types of clones that have been used in code duplication research for many years. \todo{turn it around: link the need for refactoring aids to redefining} These redefinitions aim at flagging only those clones useful for refactoring purposes.

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other techniques to be applied. Similar future measurements will provide further insight into the contexts where clones occur, and what this means for the refactoring processes. Finally, we strive to construct a \todo{a model cannot apply something} model that automatically applies refactorings for a large part of the detected duplication problems. 
% This model will be implemented for the Java programming language.
\end{abstract}

>>>>

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code, as creates explicit dependencies between fragments of code. Typically between 10 and 20 percent of projects are cloned. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. To do this, we propose a method to be able to detect clones that are suitable for refactoring. This method focuses on taking into account the scope and coupling between expressions in code, to be sure our refactoring improves the design and does not leave side effects after it is applied.

Our intermediate results indicate that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately a fifth of the duplication can be refactored through method extraction, while other clones require other techniques to be applied. Similar future measurements will provide further insight into the contexts where clones occur, and what this means for the refactoring processes. Finally, we strive to construct a tool that automatically applies refactorings for a large part of the detected duplication problems.
\end{abstract}
